\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2022-01-31 manuscript/paper.tex
Update the survival model with extracted association features from tsfresh

>>>>

To quantify the effect of the longitudinal outcomes on the risk for an event, we use a Cox~\citep{Cox1972JRSS} relative risk model of the form
\begin{equation}
  \label{eq:intensity-model}
  \lambda(t|\cM_k(t), G = k) = \lambda_0(t) \exp \Big\{\sum_{l=1}^L \sum_{a=1}^\cA {\gamma_{k,a}^l}^\top \Psi_a^l \Big\},
\end{equation}
where $\lambda_0(\cdot)$ is an unspecified baseline hazard function.

For each $l$-th longitudinal outcome, we consider $\cA \in \N_+$ known features $\Psi_a$ defining a shared association with $\gamma_{k,a}^l \in \R^{\cA}$ the corresponding joint association parameters.  These features are extracted from $Y$ by the \texttt{Python} library \texttt{tsfresh}. This can be viewed as a generalization of SREMs~\citep{rizopoulos2010jm}. Let us finally denote
\[\gamma_k= (\gamma_{k,1}^1, \ldots, \gamma_{k,\cA}^1, \ldots, \gamma_{k,1}^L, \ldots, \gamma_{k,\cA}^L )^\top \in \R^{L\cA}, \] so that
\begin{equation}
  \label{eq:def-asso-features}
  \lambda(t|\Psi, G = k) = \lambda_0(t) \exp \big\{\gamma_k^\top \Psi \big\}.
\end{equation}
